---
title: "Research"
lang: en
---

# Research Themes

- Long-term care
  - Community-oriented care
  - Care process
  - Patient-led research
    - Dementia
    - Parkinson's disease
    - Spinocerebellar Degeneration (SCD)
    - Stroke
  - Inclusive Fashion Show
- Urban planning
  - Walkable town for older adults and people with disabilities
  - Community design code
  - Utilising vacant properties
  - Niigatalogy
- Geographical information system
  - R/sf/geojp
  - QGIS plugin development

## Ageing and Urban Planning in Japan

Baba Y and Ooyama C (2025) Comprehensive community care in Japan, in 
<a href="https://www.taylorfrancis.com/books/oa-edit/10.4324/9781003144441/ageing-urban-planning-matthias-drilling-fabian-neuhaus-pamela-suero-hind-al-shoubaki?refId=bd8c5e5c-1349-430b-804c-d47dca69b7ec&context=ubx">Ageing and Urban Planning </a>



## Inclusive Fashion Show

```{r include=FALSE}
library(readr)
library(DT)
library(leaflet)
library(leaflet.extras)

df <- read_csv("data.csv", trim_ws = TRUE)

# ポップアップ表示用テキスト
popup_text <- paste0(
  "<b>Event:</b> ", df$name,
  "<br><b>Data:</b> ", df$date,
  "<br><b>Hosted by:</b> ", df$host
)

# 地図作成
m <- leaflet(data = df)

# 背景地図
m <- addProviderTiles(m, providers$CartoDB.Positron)

# マーカー追加
m <- addMarkers(
  map = m,
  lng = df$X,
  lat = df$Y,
  popup = popup_text
)
```

```{r echo=FALSE}
addFullscreenControl(m)
```

```{r echo=FALSE}
table_df <- df[, c("name", "date", "host")]

datatable(
  table_df,
  colnames = c("Event", "Date", "Hosted by"),
  options = list(pageLength = 10)
)
```

